The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-11-30 article_final/main.tex
Edited complexity bound

The per-cycle complexity is $\mathcal{O}(mn^2 + n^2k + nk^2)$, where $m \geq n$ are the dimensions of the target matrix and $k$ is the size of the retained subspace (typically $k \ll n$).

@@

\section{More details for Linear Least Squares}
\label{sec:lls_plots_section}
Tuned \texttt{lr} and \texttt{momentum} coefficients are in the \tableref{tbl:lls_lrs_app}. Spectral, nuclear norm of the gradients over iterations and loss over time are in the \figureref{fig:app_lls}. Very low speed of Fanions and F-Fanions for large $k$ is probably caused by ineffective implementation of TRLan by \cite{cupy_svds_ref}, since $\mathcal{O}(mn^2 + n^2k + nk^2)$ complexity is actually $\mathcal{O}(mn^2)$.

@@

\paragraph{Linear Least Squares and CIFAR airbench} Experiments were conducted on a single NVIDIA RTX A4000. The code was run with Python 3.10.13 and Pytorch~2.6.0+cu126.

>>>>

The per-cycle complexity is $\mathcal{O}(mn^2 + n^2d + nd^2)$, where $m \geq n$ are the dimensions of the target matrix and $d$ is the size of the retained subspace (typically $d \ll n$).

@@

\section{More details for Linear Least Squares}
\label{sec:lls_plots_section}
Tuned \texttt{lr} and \texttt{momentum} coefficients are in the \tableref{tbl:lls_lrs_app}. Spectral, nuclear norm of the gradients over iterations and loss over time are in the \figureref{fig:app_lls}. Very low speed of Fanions and F-Fanions for large $k$ is probably caused by ineffective implementation of TRLan by \cite{cupy_svds_ref}.

@@

\paragraph{Linear Least Squares and CIFAR airbench} Experiments were conducted on a single NVIDIA RTX A4000. The code was run with Python 3.10.13 and Pytorch~2.6.0+cu126 on a computer with an EPYC 7543 processor.
